Developing a preprint culture in biology

### 2012-09-28 ms.tex

% @Ethan

>>>>

PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new publishing
system that provides both a preprint server, and a peer reviewed journal.
It is focused on the the biological and medical sciences, which may help
overcome the perception that preprints do not have a home in biology.
PeerJ allows commenting on posted preprints, improving the potential
for pre-publication dialog. In addition, preprints can be made private if
the authors choose, and shared only with selected colleagues. While this
reduces some of the benefits of preprints described above, it may allow
some researchers who would not otherwise post preprints to begin to explore
the possibility in a manner appropriate to their current circumstances.

In contrast to other preprint servers users cannot post unlimited public
preprints for free. One preprint per year can be posted for free and a
onetime (i.e. lifetime) fee of 99 dollars allows the posting of unlimited
public preprints. It is also worth noting that the preprint server is not
tied to the journal, so preprints can be posted regardless of where they
will eventually be submitted for publication.
